\documentclass[12pt, a4]{article}

\usepackage[margin=1in]{geometry}
\usepackage{titlesec}

\titleformat{\section}
{\Large\bfseries}
{}
{0em}
{}[\titlerule]

\titleformat{\subsection}
{\bfseries\small}
{}
{0em}
{}

\begin{document}

\section{Mount Kenya University}
\subsection{BBM 1101: Introduction to Business Studies CAT1}
\subsection{Name: Wilfred Githuka Reg.Number: BIT2019/44664}

\textbf{Question 1. Examination of circumstances under which middlemen would be significant in the
channel of distribution.}

The market is composed of 2 main entities who facilitate the concept of
business. They are the consumers who are willing or have the purchasing ability
of buying products or services. The second party is the producers who create the
goods or services.

Between the 2 are the middlemen or intermediaries who are a vital link to ensure
the consumers get the products they need. Also they help the producers reach the
consumers.The middle men act like a bridge between the two parties.

\begin{itemize}
  
\item{Flow of Goods: Middlemen are quite important since they ensure that the
goods/services reach the consumers. They assume the risk for holding onto any
goods, or services before they reach the intended consumers. Without them, the
products would be facing a big challenge in getting to the consumers. Companies
are in the business of producing the goods/servives. Should they deviate from
this and start looking for the consumers directly, their production will suffer
immensely. Thus the market needs to have middlemen who connect the producers and
consumers.}

\item{Educate Both Parties: Middlemen due to the fact that they are in the middle
point bewteen the consumers and producers, they are better placed to advice the
opposite parties. The can advice the producers on which category of cosumers
they need to target in order to maximise sales. On the other hand, middlemen can
also advice the consumers on which products in the market are of better quality.
Thus the consumers are better educated when making choices during purchasing.
Such flow of information will benefit both partiees immensely.}

\item{Increase Reach of Products: Middlemen help small business reach the clients
faster than other means. For small business which are just starting, middlemen
come in quite handy. Middlemen also have their own sales strategy or incentives,
which help the products goods move more quickly.}

\item{Provide Variety of Choice: A middleman will stock more that one companies goods.
Normally a middleman will have a variety of goods that the consumer can choose
from. This helps in providing more choice in the market thereby reducing market
dominance by one producer flooding the market.}

\item{Stabilization of Prices: In a market that is filled with more than one
middleman, there tends to exist a form of competition between them. This will
result in a stabilisation of the prices as they try to beat each others prices.
Also any flactuation of prices from the producers will not be felt by the
consumers.}

\end{itemize}
\pagebreak

\textbf{Question 2. Disussion of pricing methods that one can employ in fixing prices}
\begin{itemize}
  
\item{Premium Pricing: Set a high price where there is uniqueness about the product.
This approach is  used where a substantial competitive advantage exists.
Such high prices are charge for human wants and not nesessarily what the
consumers needs}

\item{Penetration Pricing  When the products are introduced into the market, the
price charged for products and services is set artificially low so that to
gain market share. Once this is achieved, the price is increased to a high price.}

\item{Economy Pricing  This method is implemented when introducing a product in the
market. The price is set at an economic level, considerably low.}

\item{Price Skimming: A method used by fast moving producst like electronic gadgets.
They charge a high price because the device has features which give them some
form of advantage over other devices. Later onwards the price goes down as other
devices enter the market and competition grows.}

\item{Psychological Pricing :This approach is used when the marketer wants the
consumer to respond emotionallly to a product which the consumer finds close to
their heart. This priving method helps the marketer to fix the prices they
want.}

\end{itemize}


\textbf{Question 3. Disussion of the statement: Mergers are becoming popular 'day to
day'}
\begin{itemize}
  
\item{Mergers are becoming popular as many companies seek out ways to stay afloat of
improve their numbers in todays economic times. A merger can have many reasons
behind it but many are for marketing reasons.}

\item{When 2 companies realise there is much more potetial to increase their market
share, a merger is always a viable option. After the merger, the reultant big
company will have the combines power of the 2 which will increase market share.}

\item{Mergers are increasingly becoming popular as many companies merge to share
technology research and development. With a high risk pegged on introducing a
product with new technology, companies would rather go forward together as a
merger then share the risk.}

\item{As the market dynamics change, new young generation are dictating how companies
produce goods and servives. Tapping to this young generation is prooving
difficult for old companies which would rather merge with a young comany which
understand the market better inorder to boost sales.}

\item{Companies are finding merger making more sense in order to survive the rapid
economic changes that is happening. Many corporations are using mergers so that
to gain larger market control and offer better products. A merger wether
horizontal or vertical ensures that both parties bring value onto the table for
the resultant merger to be viable.}

\end{itemize}

\end{document}